---
title: "Lab 2"
author: "Eric Gleiter: Github- Eric-Gleiter"
date: "2/3/2020"
output: html_document
---

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco)
```

Question 1) 
```{r}
date <- choco$Review.Date
ratings <- choco$Rating
locations <- choco$Company.Location

numChoco <- length(ratings)
numChoco
```
There are 1852 chocolate bars that have been rated




Question 2)
```{r}
counts<-table(choco$Review.Date)
plot(date,ratings)
barplot(counts)

```
The number of ratings increased with year up until 2016 when it started to drop. 

Question 3)

Question 3
```{r}
counts <- table(choco$Company.Location, choco$Rating)
counts
```
The top three countries are The USA, Canada, and France, then looking at the table we can see all three countires have the most ratings at 3.5 and the a "normalish" spread about that point. Except for the us is has two peaks in its data, it also has the most data points which would be the cause.

Question 4)
Which company produces the standard highest rated chocolate?

Question 5)
```{r}
counts <- table(choco$Company, choco$Rating)
counts
```
based on the table we see that valrhona and soltice have a hogh rating as they have a lot of ratings in the higher portion of the ratings table 